### 2019-02-19 sections/introduction.tex
small fixes in intro

Users can work together in a number of ways, and this is reflected in \TOP by task compositions.
There is sequential composition, parallel composition, and choice.
Users need to communicate in order to engage in these forms of collaboration.
This is reflected in \TOP by three kinds of communication mechanisms.
There is data flow \emph{alongside} control flow, where the result of a task is passed onto the next.
There is data flow \emph{across} control flow, where information is shared between multiple tasks.
Finally, there is communication with the \emph{outside} world, where information is entered into the system via input events.
The end points where the outside world interacts with \TOP applications are called editors.
In generated applications, editors can take many forms, like input fields, selection boxes, or map widgets.

\fixme{Change if title changes.}
In this paper we study the essence of \TOP.
We claim that at the heart of \TOP lie modular interactive workflows.
Workflows because \TOP programs coordinate collaboration between people.
Interactive because progress of \TOP programs is driven by user input.
Modular because the embedding in a strongly-typed functional language allows powerful abstractions using type-driven techniques and higher-order functions.

@@

@@

In this paper we aim to identify the essence of \TOP in formal as well as an informal way.
These core principles lead to a formal system for \TOP called \TOPHAT.
\TOPHAT paves the way to formal reasoning about applications written using the \TOP paradigm,
like those in \ITASKS and \MTASKS.

@@

>>>>

Users can work together in a number of ways, and this is reflected in \TOP by task compositions.
There is sequential composition, parallel composition, and choice.
Users need to communicate in order to engage in these forms of collaboration.
This is reflected in \TOP by three kinds of communication mechanisms.
There is data flow \emph{alongside} control flow, where the result of a task is passed onto the next.
There is data flow \emph{across} control flow, where information is shared between multiple tasks.
Finally, there is communication with the \emph{outside} world, where information is entered into the system via input events.
\fixme{Should this be mentioned earlier?}
The end points where the outside world interacts with \TOP applications are called editors.
In generated applications, editors can take many forms, like input fields, selection boxes, or map widgets.

@@

\fixme{Rewrite}

@@

In this paper we aim to identify the essence of \TOP in formal as well as an informal way.
These core principles lead to a formal system for \TOP, called \TOPHAT,
which paves the way to formal reasoning.
Applications written using the \TOP paradigm, like those in \ITASKS and \MTASKS, currently lack such a feature.

@@

\fixme{Change or remove.}
In this paper we study the essence of \TOP.
We claim that at the heart of \TOP lie modular interactive workflows.
Workflows because \TOP programs coordinate collaboration between people.
Interactive because progress of \TOP programs is driven by user input.
Modular because the embedding in a strongly-typed functional language allows powerful abstractions using type-driven techniques and higher-order functions.
